%implementing document formatting:
\input{preamble.tex}
\usepackage{enumitem}
\setlist{leftmargin=5.5mm}
%Vectors
\renewcommand{\vec}[1]{\boldsymbol{\mathbf{#1}}}

\begin{document}
\renewcommand\chaptername{KAPITEL}
\renewcommand\contentsname{Indhold}
\renewcommand\figurename{Figur}
\renewcommand\tablename{Tabel}

\section*{Review of Paper on\\
Automated Convoying of Trucks Utilizing Waypoints\\
\small Wednesday, 30th of November 2016}
\subsection{Overall Assessment}
The paper is well written and the figures are clear to understand. The flow is nice, and the reader felt well informed during the entire paper.
\vspace{-6pt}
\subsection{General Comments}
E-mail addresses could be included in the header. Maybe the specific address is not necessary.\\

\vspace{-7pt}\noindent
The paper is generally well structured.\\

\vspace{-7pt}\noindent
We think, that when you are going to write the results section, the content and structure of the presented results  must reflect the subsections within the method section. \\

\vspace{-7pt}\noindent
Since the language of the paper is American English, the headline should appear with capital letters for the important words, same as in the title of these corrections.
\vspace{-6pt}
\subsection{Specific Comments}
\begin{itemize}
  \item[-] Section I - 2nd column - 3rd paragraph: "[...] this paper is a proof of concept."\\
  \textbf{Suggestion:} "[...] this prototype is a proof of concept."

  \item[-] Section II - \\
	\textbf{Note:} It is considered good practice to use a header, or implement the subsections as sections instead.

  \item[-] Section II A - 1st column - 1st paragraph: "[...] drives as precise in the tracks [...]"\\
  \textbf{Suggestion:} "drive" instead of "drives". Maybe use "route" instead of "tracks".

  \item[-] Section II A - 1st column - 3rd paragraph: "[...] from one waypoint the to next in a straight line."\\
	\textbf{Suggestion:} "to the" instead and "next one" instead only "next".

	\item[-] Section II B - 2nd column - 1st paragraph: "It ensures no packet loss if a connection is available."\\
	\textbf{Note:} TCP does not ensure no packet loss. 

	\item[-] Section II E.1 - 2nd column - 1st paragraph: "[...] and thereby there should always be a way to obtain the same state for TB2."\\
	\textbf{Suggestion:} "and it should therefore be possible to obtain the same state for TB2."

	\item[-] Section II E.1 - 2nd column - 1st paragraph: "[...] approach will handle take the dynamics [...]"\\
	\textbf{Suggestion:} Remove handle.

	\item[-] Section II E.2 - 2nd column - 1st paragraph: "This as the following:"\\
	\textbf{Suggestion:} Remove.

	\item[-] Section II E.2 - 1st column - after figure 7: "[...] every run-through, since the system [...]"\\
	\textbf{Suggestion:} "[...] every run-through, as the system [...]"

	\item[-] Section II F - 1st column - 1st paragraph: "[...] route that the TB1, such that [...]"\\
	\textbf{Suggestion:} "[...] route for the TB1, such that [...]"
\end{itemize}

\end{document}